### 2019-02-19 sections/relatedwork.tex
add Cooper and Krishnasmurti
added fixme's
add Meyerovich et al
cite FrTime and Flapjax

@@

The idea of \FRP was pioneered by \citet{conf/icfp/ElliottH97}, in the meantime there are many variants and implementations, with reactive-banana one of the most well-known \cite{reactive-banana}.

>>>>

\fixme{Intro related work}

@@

The idea of \FRP was pioneered by \citet{conf/icfp/ElliottH97}.
In the meantime there are many variants and implementations, where reactive-banana \cite{reactive-banana}, FrTime \cite{CooperK04}, and Flapjax \cite{conf/oopsla/MeyerovichGBCGBK09} belong to the most well-known.
